---
title: "Mine Data"
Author: Yiyang Jiang
---

# Journal Analysis Report

This report shows the results of two analytical queries against our MySQL data warehouse.

## Analytical Query I: Top Five Journals with the Most Articles Published

The following query retrieves the top five journals with the most articles published in them for the time period:

```{r}
library(RMySQL)   

db_user <- 'yiyangjiang'
db_password <- 'Jyy123456'
db_name <- 'SandboxDB'
db_host <- 'cs5200-p2.cmwnfqdoq8fo.us-west-2.rds.amazonaws.com' 
db_port <- 3306 # always this port unless you change it during installation

# 3. Connect to DB
mydb <-  dbConnect(MySQL(), user = db_user, password = db_password,
                   dbname = db_name, host = db_host, port = db_port)
```
The following query retrieves the top five journals with the most articles published in them for the time period:
```{sql connection=mydb}
SELECT Title, NumArticles
FROM journal_fact
ORDER BY NumArticles DESC
LIMIT 5;
```
### Retrieve the data from the MySQL data warehouse
```{r}
query <- "SELECT Title, NumArticles
          FROM journal_fact
          ORDER BY NumArticles DESC
          LIMIT 5"

top_journals <- dbGetQuery(mydb, query)
```

### create a bar chart to visualize the result
```{r}
library(ggplot2)
ggplot(top_journals, aes(x = reorder(Title, -NumArticles), y = NumArticles, fill = Title)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Top Five Journals with the Most Articles Published",
       x = "Journal Title",
       y = "Number of Articles") +
  theme(axis.text.x = element_text(angle = 60, hjust = 1),
        legend.position = "none") +
  scale_fill_brewer(palette = "Set1")
```

## Analytical Query II: Number of Articles per Journal per Year Broken Down by Quarter

The following query retrieves the number of articles per journal per year broken down by quarter:
```{sql connection=mydb}
SELECT Title, PubDateYear, PubQuarter, SUM(NumArticles) as TotalArticles
FROM journal_fact
GROUP BY Title, PubDateYear, PubQuarter
ORDER BY PubDateYear ASC, PubQuarter ASC;
```
### Retrieve the data from the MySQL data warehouse
```{r}
query <- "SELECT Title, PubDateYear, PubQuarter, SUM(NumArticles) as TotalArticles
          FROM journal_fact
          GROUP BY Title, PubDateYear, PubQuarter
          ORDER BY PubDateYear ASC, PubQuarter ASC"

data <- dbGetQuery(mydb, query)
```

### create a bar chart to visualize the result
```{r}
data$PubDate <- paste0(data$PubDateYear, "-Q", data$PubQuarter)
data$PubDate <- as.factor(data$PubDate)

# Step 5: Create the visualization
ggplot(data, aes(x = PubDate, y = TotalArticles)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Total Articles per Journal by Year and Quarter",
       x = "Year and Quarter",
       y = "Total Articles") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```



